Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-08-16 Ben_Manuscripts/structure_paper/Draft.tex
Lots of draft updates

@@

  We further refined our structural understanding of the system by simulating X-ray 
  diffraction patterns produced from equilibrated MD trajectories and comparing them
  to experiment. We tested systems built with 5 columns per pore in the parallel 
  displaced and sandwiched configurations at 300 K in the ordered and disordered
  basins. We generated simulated patterns using the equilibrated portion of each 
  simulation trajectory. 
  %MRS11: probably want to say about about HOW they were generated (Could refer back to methods?)
  %MRS11: my pass below.
  There are two important factor to take into account when looking at differences between experimental XRD and simulated XRD.  First, the 
  simulated diffraction patterns have some noise, especially
  along the $q_z$ axis at $q_r$=0, which is where several of the more interesting features are located.
  This is due to the angle averaging the 3D structure factor around the $q_z$-axis (see section~\ref{method:xrd}), meaning there are fewer samples as  $q_r$ approaches 0. The amount of samples to converge along the $q_z$ axis is analyzed in Supporting Information section S-\ref{S-section:xrd_noise}. 
  More importantly, are simulations do not appear to be long 
  enough to sample 
  truly independent configurations within their respective metastable basins
  (See section~\ref{section:slow_dynamics}), meaning we must take care in interpreting the results of the XRD. 
  %MRS11: the fact that they are not within their metastable basis DOESN'T just affect the noise it affects everything else.  If we had 100 times longer, it would reduce the noise along the z axis a lot, but the peaks would likely still be too intense, as we would have a lot of data long the z, but still be in the timescales that are too slow to reduce the peak intensity. Did a pass above.
The simulated patterns generated for all systems
  studied are shown and compared to experiment in Figure~\ref{fig:XRDsim}.

@@

  In the next few subsections, we have individually address each major reflection, and the similarities and differences between simulation and experiment. We start with relatively 
  uncomplicated analyses of reflection that are very similar between experiment and simulation:
  %BJC10: Could make the following more descriptive. For example : "The location of R-alkanes", "The intensity of R-pores", "The origin of R-spots", "The shape and intensity of R-pi", "The origin of R-double".
  %MRS11: that sounds good.
  \begin{itemize}
  	\item R-alkanes (section~\ref{section:ralkanes})
  	\item R-pores (section~\ref{section:rpores})
  \end{itemize}
  and then move onto more complicated explanations of those reflections whose characteristics
  do not match, or have not been fully explained by experiment:
  \begin{itemize}
  	\item R-spots (section~\ref{section:rspots})
  	\item R-$\pi$ (section~\ref{section:rpi})
  	\item R-double (section~\ref{section:rdouble})
  \end{itemize}

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{c|ccccc}
  \toprule
 		     & \multicolumn{5}{c}{Normalized Reflection Intensity}                   \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes  & 1.0        &  1.0       &  1.0      & 1.0        & 1.0                \\
  R-pores    & 12.3       &  49.5      &  54.0     & 50.8       & 53.4               \\
  R-spots    & 1.3        &  1.3       &  1.2      & 1.1        & 1.2                \\
  R-$\pi$    & 2.8        & 44.0       &  7.7      & 8.4        & 10.1               \\
  R-double   & 0.9        &  --        & --        &  --        & --                 \\ 
  \hline
   		     & \multicolumn{5}{c}{Reflection Location ($|\mathbf{q}|~\AA^{-1}$)}     \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes  & 1.39       &  1.44      &  1.44     & 1.42       & 1.43               \\  
  R-pores    & 0.176      &  0.170     &  0.170    & 0.173      & 0.172              \\
  R-spots    & 1.39       &  1.44      &  1.44     & 1.42       & 1.43               \\
  R-$\pi$    & 1.70       &  1.41      &  1.42     & 1.40       & 1.40               \\
  R-double   & 0.85       &  --        & --        &  --        & --                 \\ 
  \bottomrule
  \end{tabular}
  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
  than experiment and R-spots reflections that are slightly lower than experiment. R-double
  does not appear in any patterns, and thus has no measurable intensity.}
  \label{table:relative_inensities_300K} 
  \end{table}

@@

  \subsubsection{R-alkanes}\label{section:ralkanes}

  R-alkanes appears close to its expected location. In all cases, the maximum intensity
  of R-alkanes appears at a $|\mathbf{q}|$ value slightly higher than experiment. 
  We expect that the exact location of R-alkanes will not be perfect in our simulations
  since the simulated diffraction patterns are interpolated between a finite number of
  bins in each frequency dimension. We can achieve higher resolution with a larger
  system size, however we are satisfied with the packing distances shown by our simulations.
  %BJC10: I could integrate a 3D correlation function to get a better value

  We believe that R-alkanes is the experimental feature most likely to be reproduced by
  our simulations. For this reason we normalized the experimental and simulated diffraction
  patterns so that the average intensity within the R-alkanes is equal to 1.

  \subsubsection{R-pores}\label{section:rpores}

   R-pores is about 4 times more intense than experiment in all simulated systems. 
   %BJC10: trying to come up with a good explanation.

   We are not concerned with exactly reproducing the intensity of R-pores since it is a 
   product of long distance correlation between pores. We are primarily concerned with
   the structure within pores which is better described by reflections at higher 
   $|\mathbf{q}|$ values. The location of R-pores \textit{is} important because we can 
   use it to learn the number of monomer columns within each pore as we did in 
   section~\ref{section:mon_per_pore}

  \subsubsection{The origin of R-spots}\label{section:rspots}
%MRS10: I rephrased the below, check the diffs.
  In order to more clearly study R-spots, we equilibrated an ordered basin sandwiched 
  configuration at 280K. Many force fields do not obtain the correct equilibrium structure
  at precisely the experimental temperature. Wang et al. highlighted the shortcoming of 
  some of the most popular protein force field in predicting the temperature dependence 
  of protein structural ensembles \cite{wang_building_2017}. It is therefore possible that   % page 12
  our membrane system, simulated at 300K, is overly structured compared to the experimental
  structure at 300K. We found that lowering the temperature better resolved R-spots 
  (Figure~\ref{fig:sandwiched280K}), suggesting that our 'effective' temperature might 
  indeed be too high, overstabilizing structure. 
%  The relative intensity 
%  of R-spots in this system is slightly higher than experiment (1.5 vs. 1.3)

%  We observe an increase in the intensity of R-spots when we simulate systems at 280K. R-spots
%  is most intense in the ordered basin sandwiched configuration (Figure~\ref{fig:sandwiched280K}). 
%  The relative intensity of R-spots is slightly higher than in experiment (1.5 vs. 1.3). R-double 
%  is still not present. We will use the system simulated at 280K to more thoroughly explore the 
%  origin of R-spots.

  Evidence from the simulations strongly suggests that the R-spots signal is not a 
  result of alkane chain tilt. Previous literature has attributed the spots in 
  this particular WAXS dataset as the product of tilted alkane chains~\cite{feng_scalable_2014}.
  We measured the tilt angle of the alkane chains of the 280K system and showed
  that it equilibrates to an average tilt angle of -2\degree~(Fig.~\ref{fig:tilt}),
  far from the 37\degree~tilt angle previously used to explain R-spots.

  %To understand the most likely origin of R-spots, we determined which atoms
  %gave rise to the feature. 
  Although the monomer tails do not tilt, R-spots still originates from the 
  them. By removing all non-tail atoms from the trajectory and simulating a
  diffraction pattern with the remaining atoms, we were able to isolate the
  cause of the spots to the tails (Figure~\ref{fig:tails_rzplot}).

  %BJC9: I think Matt gets confused here. I put a more detailed explanation in 
  % the supplemental information. Do you think that's enough, or should I add
  % to this figure?
  %MRS10: rephrased.
  The evidence strongly suggests that R-spot pattern occurs because tails pack 
  together hexagonally. We plotted the center of masses of the first four tail 
  atoms of each tail originating from each head group (Figure \ref{fig:centroids}).
  We measured the angle between each center of mass and its nearest neighbor 
  center of masses with respect to the $xy$ plane of the membrane. We see distinct
  peaks in the distribution of these angles located ca. $-60\degree$, $0\degree$,
  and $60\degree$ which is consistent with a hexagonally packed configuration 
  (Figure~\ref{fig:layered_tails}). 
  %MRS10: is it importat that the ordering dies off? IF there is ordering, it will show in the spectra, and it doesn't matter that it dies off in other parts of the spectra.
  %BJC10: I only addressed this because Matt wanted a more thorough characterization of tail order 
This ordering dies off at the tail ends,
  where there is more space to fill causing them to pack nearly isotropically.
  See Section~S-\ref{S-tail_packing} for a more detailed explanation of the 
  calculation and packing distributions generated from different sections of
  the tails.

@@

% BJC5: omit for now
%  The evidence supports the hypothesis that alkane chain tails pack in a
%  hexagonal array. Groups of three tails associated with each monomer prefer to
%  sit between tails of vertically stacked monomers rather than stacking directly
%  on top of them (Figure~\ref{fig:hex_tails}). This type of packing has been seen
%  before in XRD studies of hydrocarbon chains~\cite{small_lateral_1984}.

% BJC6 : added better justification to beginning of section
%  %MRS7: couple -> ``two main''?
%%MRS7: what is the purpose of this paragraph?  I think most people would know why a lower T simulation would be more ordered (though the degree is not known).
%  There are two reasons why we see stronger ordered chain packing at 280 K compared to
%  experimental conditions of 300 K.
%  \begin{enumerate}
%  		\item The difference between 280 K and 300 K is relatively small. Our forcefield parameters
%  		may not correctly model the behavior of the tails at 300 K (citation?).
%                % look for papers on protein folding temperature dependence: see Lee-Ping Wang's AMBER-15fb paper
%  		\item Monomers aren't as confined at 300 K in our simulations versus experiment.
%  		If the head groups packed 3.7 \AA~apart, the tails would be more confined and forced
%  		to pack between vertically adjacent monomer tails. In our case, the tail region is
%  		less dense than experiment which gives the tails freedom to organize in a more
%  		entropically favored disordered state. 
%  \end{enumerate}

@@

  \subsubsection{Discrepancies between experimental and simulated R-$\pi$}\label{section:rpi}
  %MRS10: in the list of questions above, you just talk about intensity, but this title talks about more discrepnacies. It could go either way (as I mention before, there's the issue of R-pi placement, too), but it should be consistent.
  The simulated intensity of R-$\pi$ at 300K is more intense relative to the experimental 
  system. The difference in intensity ranges from 3 times too high in the ordered parallel
  displaced system to 15 times too high in the ordered sandwiched configuration 
  (Table~\ref{table:relative_inensities_300K}).
  %MRS10: should specify this is in the 300 K simulations.

  The peak shape of the $q_r$ cross-section of R-$\pi$ in the simulated XRD is qualitatively different
  from experiment (Figures~\ref{fig:exp_rsection_fit} and~\ref{fig:sim_rsection_fit}).
  We use simulated XRD generated from the ordered parallel displaced configuration
  as an example in Figure~\ref{fig:rpi_exp_comparison}. The $q_z$ cross-section 
  fits a Lorentzian profile relatively well, although its full width at half maximum
  (FWHM) is 48\% broader than the experimental cross-section 
  (Figures~\ref{fig:exp_zsection_fit} and ~\ref{fig:sim_zsection_fit}). We attempted
  to fit a Lorentzian profile to the $q_r$ cross-section and although the FWHM agrees
  with experiment within error, the fit is not optimal due to the three sharp peaks
  that appear near $q_r$ = 0.

  An exact quantitative comparison between experiment and simulation is not feasible for several reasons. 
  Experimental peaks broaden due to effects that we can not easily simulate such
  as finite size crystalline domains and instrumental resolution. In our simulated
  XRD patterns, the system size imposes limitations on the resolution, which makes
  it difficult to reliably fit peaks. This is especially problematic when comparing
  the FWHM of the $q_z$ cross-section of R-$\pi$, where the experimental FWHM 
  (0.11 $\AA^{-1}$) is similar to the bin size in the $q_z$ direction (ca. 0.07 $\AA^{-1}$).
  Additionally, we model each atom with a Gaussian sphere of electron density. 
  The true electronic structure is likely much more complicated. However, we can
  explore reasons for which differences in the simulation structure could change
  the peak shapes to be in better agreement with experiment.

  %MRS9: State explicitly in what way the discrepancy would increase, i.e. experimental FWHM are broadened by other source (doppler pressure, insttrument broadening) that do no affect the simulated spectra, the experimental spectra may be even narrower than spectra generated from simulations are.  
  %MRS9: one question, do any of the approximations used in the simulation actually lead to broadening that would not be in experiment (gaussian scatterers, etc.  Also, (semi-related) do Gaussian scatters lead to Gaussian peaks? Fourier transforms of Gaussians are Gaussians) 
  % BJC8: Can add more detail about different types of broadening - instrument / finite resolution broadening (for
  % experimental case), doppler (gaussian shaped) and pressure broadening (Lorentzian shaped)
  % See: https://www.nist.gov/pml/atomic-spectroscopy-compendium-basic-ideas-notation-data-and-formulas/atomic-spectroscopy-7
  %MRS 9: it is a little problematic to use two different types of fit, as the FWHM is a little different for each of then. Would lead to slight discrepancies from that.  FWHM is a natural scale parameter for Lorenzians, but not really for Gaussian.

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{exp_rsection_fit.png}
  \caption{FWHM = 0.792 $\pm$ 0.009 $\AA^{-1}$}\label{fig:exp_rsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sim_rsection_fit.png}
  \caption{FWHM = 0.796 $\pm$ 0.011 $\AA^{-1}$}\label{fig:sim_rsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{exp_zsection_fit.png}
  \caption{FWHM = 0.110 $\pm$ 0.003 $\AA^{-1}$}\label{fig:exp_zsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sim_zsection_fit.png}
  \caption{FWHM = 0.163 $\pm$ 0.011 $\AA^{-1}$}\label{fig:sim_zsection_fit}
  \end{subfigure}
  \caption{
%  There are clear qualitative differences between the experimental WAXS pattern 
%  ((a) and (c)) and the simulated XRD pattern resulting from simulations 
%  of the ordered parallel displaced configuration ((b) and (d)). 
    %MRS10: don't make the thesis what was done, but what the reader should know. 
  We compared the experimental WAXS pattern ((a) and (c)) to the simulated XRD
  pattern resulting from simulations of the ordered parallel displaced 
  configuration ((b) and (d)). The $q_r$ cross-section of R-$\pi$ ((a) and (b))
  is qualitatively different between experiment (a) and simulation (b). We fit
  Lorentzian profiles to each peak and the FWHM of the simulated pattern agrees
  with experiment within error, however the fit to the simulated data is 
  obscured by the three sharp peaks which appear near $q_r$ = 0. The $q_z$ 
  cross-sections of R-$\pi$ ((c) and (d)) are qualitatively similar. Each fits
  a Lorentzian profile well, however the FWHM of the simulated cross-section (d)
  is 48\% larger than the experimental cross-section.}\label{fig:rpi_exp_comparison}
  \end{figure}

  We have identified a number of potential ways that simulation conditions,
  forcefield and initial configurations could affect the intensity and shape of
  R-$\pi$, and assess each using a simplified model of the pore. Our simplified model 
  represents each monomer head group as a single point and places them in either
  a parallel displaced or sandwiched configuration. We chose to explore the 
  influence of thermal noise in each dimension, the effect of $z$-direction 
  distance correlations between scatterers within columns, as well as correlation
  between columns since these are the variables we believe have the largest 
  influence on peak shape and intensity.

>>>>

  \subsection{Simplified Systems}\label{method:simple_systems}

  In order to gain a deeper understanding of discrepancies between the experimental and
  and simulated R-$\pi$ reflection, we used a simplified baseline model where we 
  represent each monomer as a single point scatterer located at the center of mass
  of its head group. In order to make a system approximately similar to our equilibrated 
  simulation geometries, we created 4 hexagonally packed pore regions spaced 42.5 \AA 
  apart, each with 5 columns of scatterers spaced 4.4 \AA apart in the $z$-direction. We
  built the system 4 times taller in the $z$-direction (80 scatterers per column) in order
  to access higher $q_z$ resolution.

  We gave the simplified models the same amount of disorder present in the atomistic
  simulations. We observe two sources of disorder: thermal motion of atoms
  and quenched disorder which is created by rapid structural rearrangement during 
  early equilibration and is largely locked into place for the remainder of the 
  simulation. We measured thermal disorder by calculating the standard deviation of 
  the distribution of head group center of mass positions from their average positions.
  We measured quenched disorder by calculating the standard deviation of the distribution
  of head group center of masses from their idealized average positions. In the 
  $z$-direction, we measured the deviation of the head group center of masses from an
  equally spaced column of head groups. In the $xy$ plane, we calculated the standard 
  deviation in radial position from the pore center and the angular deviation from 
  equally spaced points surrounding the pore center. This method for calculating 
  quenched order inherently includes thermal disorder.

  We approximated interactions between particles by correlating the $z$-distance 
  between points within each column of point scatterers. We placed points in each
  column by drawing random samples from a multivariate normal distribution defined
  by the mean positions of an equally spaced column of points. We gave the 
  distribution at each point along the column the same standard deviation, 
  $\sigma_z$ and we defined a covariance matrix such that the covariance, $v$, of
  the distance, $d$, between scatterers decays exponentially from $v$ according
  to the equation $ve^{-d/L}$, where $L$ is the correlation length. We used the
  experimental correlation length of 9.0 $\AA$.

  We calculated averaged R-$\pi$ profiles by simulating the diffraction pattern
  of trajectories consisting of 1000 independent simple system configurations 
  generated with point scatterer placement based on the quenched order seen in
  atomistic simulations. The quenched disorder is greater in  magnitude than thermal 
  disorder (See Table~\ref{table:quenched_disorder} in section~\ref{section:rpi})
  and inherently includes thermal disorder due to the way we calculate it.
  This method assumes that the timescales for large scale rearrangements of the
  system are much longer than what we can feasibly simulate.

@@

  We further refined our structural understanding of the system by simulating X-ray 
  diffraction patterns produced from equilibrated MD trajectories and comparing them
  to experiment (see section~\ref{method:xrd}). We tested systems built with 5 columns
  per pore in the parallel displaced and sandwiched configurations at 300 K in the 
  ordered and disordered basins. We generated simulated patterns using the equilibrated
  portion of each simulation trajectory. There are two important factors to take into
  account when looking at differences between experimental XRD and simulated XRD. First,
  the simulated diffraction patterns have some noise, especially along the $q_z$ axis 
  at $q_r$=0, which is where several of the more interesting features are located. This
  is due to the angle averaging of the 3D structure factor around the $q_z$-axis, meaning
  there are fewer samples as  $q_r$ approaches 0. The amount of samples to converge along
  the $q_z$ axis is analyzed in Supporting Information section S-\ref{S-section:xrd_noise}. 
  More importantly, our simulations do not appear to be long enough to sample truly 
  independent configurations within their respective metastable basins (See 
  section~\ref{section:slow_dynamics}), meaning we must take care in interpreting the
  results of the XRD. The simulated patterns generated for all systems studied are shown
  and compared to experiment in Figure~\ref{fig:XRDsim}.

  %MRS11: the fact that they are not within their metastable basis DOESN'T just affect the noise it affects everything else.  If we had 100 times longer, it would reduce the noise along the z axis a lot, but the peaks would likely still be too intense, as we would have a lot of data long the z, but still be in the timescales that are too slow to reduce the peak intensity. Did a pass above.

@@

  In the next few subsections, we individually address each major reflection, and the
  similarities and differences between simulation and experiment. We start with relatively 
  uncomplicated analyses of reflections that are very similar between experiment and simulation:
  \begin{itemize}
  	\item The location of R-alkanes (section~\ref{section:ralkanes})
  	\item The intensity of R-pores (section~\ref{section:rpores})
  \end{itemize}
  and then move onto more complicated explanations of those reflections whose characteristics
  do not match, or have not been fully explained by experiment:
  \begin{itemize}
  	\item The origin of R-spots (section~\ref{section:rspots})
  	\item The position, shape and intensity of R-$\pi$ (section~\ref{section:rpi})
  	\item The origin of R-double (section~\ref{section:rdouble})
  \end{itemize}

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{c|ccccc}
  \toprule
 		     & \multicolumn{5}{c}{Normalized Reflection Intensity}                   \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes  & 1.0        &  1.0       &  1.0      &  1.0       &  1.0               \\
  R-pores    & 12.3       & 49.5       & 54.0      & 50.8       & 53.4               \\
  R-spots    & 1.2        &  1.2       &  1.2      &  1.1       &  1.1               \\
  R-$\pi$    & 2.8        & 44.0       &  7.7      &  8.4       & 10.1               \\
  R-double   & 0.9        &  --        & --        &  --        & --                 \\ 
  \hline
   		     & \multicolumn{5}{c}{Reflection Location ($|\mathbf{q}|~\AA^{-1}$)}     \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes  & 1.39       &  1.44      &  1.44     & 1.42       & 1.43               \\  
  R-pores    & 0.176      &  0.170     &  0.170    & 0.173      & 0.172              \\
  R-spots    & 1.39       &  1.44      &  1.44     & 1.42       & 1.43               \\
  R-$\pi$    & 1.70       &  1.41      &  1.42     & 1.40       & 1.40               \\
  R-double   & 0.85       &  --        & --        &  --        & --                 \\ 
  \bottomrule
  \end{tabular}
  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
  than experiment and R-spots reflections that are slightly lower than experiment. R-double
  does not appear in any patterns, and thus has no measurable intensity.}
  \label{table:relative_inensities_300K} 
  \end{table}

@@

  \subsubsection{The location of R-alkanes}\label{section:ralkanes}

  We normalized the experimental and simulated diffraction patterns so that the average
  intensity within R-alkanes is equal to 1 because we believe that R-alkanes is the
  experimental feature most likely to be reproduced by our simulations.
  %BJC11: could add some support of this statement - perhaps a reference to the original
  % GAFF forcefield paper? Need to actually check it though.

  R-alkanes appears close to its expected location. In all cases, the maximum intensity
  of R-alkanes appears at a $|\mathbf{q}|$ value only slightly higher than experiment. 
  We expect that the exact location of R-alkanes will not be perfect in our simulations
  since the simulated diffraction patterns are interpolated between a finite number of
  bins in each frequency dimension. We can achieve higher resolution with a larger
  system size, however we are satisfied with the packing distances shown by our simulations.
  %BJC11: I could integrate a 3D correlation function to get a better value

  \subsubsection{The location and intensity of R-pores}\label{section:rpores}

  R-pores is about 4 times more intense than experiment in all simulated systems. We
  hypothesize that this is primarily due to the relatively perfect infinite hexagonal
  array of pores in the simulated systems. In the real system, periodicity of the 
  hexagonal array is disrupted by misalignment of the crystalline domains and the
  pore-to-pore distances fluctuate more over long time scales. 
  % BJC11: Using simple systems, I can show that more highly fluctutating pore-to-pore
  % distances will decrease the intensity of R-pores. I don't think its worth getting
  % into in the main text. It's the same idea as how increased z-noise decreases the intensity of R-pi
  % BJC11: I also think that domain misalignment in the z-direction contributes. If you
  % imagine a hexagonal array of pores aligned along the z-axis, then rotate that axis
  % so it has an x and y component, then there will be constructive interference perpendicular
  % to that axis at non-zero qz values. That is why R-pores is arced. It's a different
  % type of broadening than R-pi - I think
  % BJC11: I don't think a deep dive into this is worth it. It's dependent on things
  % unrelated to the actual pore structure.

  We are not concerned with exactly reproducing the intensity of R-pores since it is a 
  product of long distance correlations between pores. We are primarily concerned with
  the structure within pores which is better described by reflections at higher 
  $|\mathbf{q}|$ values.

  The location of the leading peak of R-pores is geometrically related to the average 
  distance between pores. However, there is uncertainty in its exact location because
  the Fourier bin size is so large. We can measure the average distance between columns
  with more precision in real space (See Section~\ref{method:pore_spacing}). We showed
  that we achieve experimentally consistent pore spacings in our simulations in 
  Section~\ref{section:section:mon_per_pore}.

  \subsubsection{The origin of R-spots}\label{section:rspots}

  The intensity of R-spots is close to experiment when generated from any of our
  simulated systems. The appearance of R-spots is inconspicuous in most cases so we
  assumed that the location of R-spots, in terms of $|\mathbf{q}|$ would coincide with
  that of R-alkanes, and that it's $q_z$ location should be roughly in line with 
  R-double (half the $q_z$ location of R-$\pi$) as it appears in the experimental pattern.
  We measured the intensity of R-spots by radially integrating the simulated
  diffraction pattern between $1.4~\AA^{-1} < |\mathbf{q}| < 1.57~\AA^{-1}$ (between
  4 and 4.5 $\AA$ in real space) and then locating and recording the intensity of the 
  appropriate peaks in the resulting distribution.

  R-spots is most likely a result of ordered packing of the monomer's alkyl tails. 
  Previous literature has attributed the spots in this particular WAXS dataset as 
  the product of tilted alkane chains~\cite{feng_scalable_2014}. Here we refute 
  that explanation and show that the tails do not tilt, but rather pack in a 
  hexagonal array.

  In order to more clearly study R-spots, we equilibrated an ordered basin sandwiched 
  configuration at 280K. Many force fields do not obtain the correct equilibrium structure
  at precisely the experimental temperature. Wang et al. highlighted the shortcoming of 
  some of the most popular protein force field in predicting the temperature dependence 
  of protein structural ensembles \cite{wang_building_2017}. It is therefore possible that   % page 12
  our membrane system, simulated at 300K, is under-structured in the tail region compared
  to the experimental structure at 300K. We found that lowering the temperature better 
  resolved R-spots (Figure~\ref{fig:sandwiched280K}), suggesting that our 'effective' 
  temperature might indeed be too high, understabilizing structure.

  Evidence from the simulations strongly suggests that the R-spots signal is not a 
  result of alkane chain tilt. We measured the tilt angle of the alkane chains of
  the 280K system and showed that it equilibrates to an average tilt angle of
  -2\degree~(Fig.~\ref{fig:tilt}), far from the 37\degree~tilt angle previously
  used to explain R-spots.

  Although the monomer tails do not tilt, R-spots still originates from 
  them. By removing all non-tail atoms from the trajectory and simulating a
  diffraction pattern with the remaining atoms, we were able to isolate the
  cause of the spots to the tails (Figure~\ref{fig:tails_rzplot}).

  %BJC11: need to rephrase -- "strongly suggests" used two paragraphs prior
  The evidence strongly suggests that R-spots occurs because tails pack 
  together hexagonally. We plotted the center of masses of the first four tail 
  atoms of all tails (Figure \ref{fig:centroids}). We measured the angle between
  each center of mass and its nearest neighbor center of masses with respect to
  the $xy$ plane of the membrane. We see distinct peaks in the distribution of
  these angles located ca. $-60\degree$, $0\degree$, and $60\degree$ which is
  consistent with a hexagonally packed configuration (Figure~\ref{fig:layered_tails}). 
  %MRS10: is it importat that the ordering dies off? IF there is ordering, it will show in the spectra, and it doesn't matter that it dies off in other parts of the spectra.
  %BJC10: I only addressed this because Matt wanted a more thorough characterization of tail order 
  This ordering dies off at the tail ends, where there is more space to fill 
  causing them to pack nearly isotropically. See Section~S-\ref{S-tail_packing}
  for a more detailed explanation of the calculation and packing distributions
  generated from different sections of the tails.

@@

@@

  \subsubsection{The position, shape and intensity of R-$\pi$}\label{section:rpi}

  The position, shape and intensity of R-$\pi$, generated from simulations at 300K, are 
  qualitatively and quantitatively different than experiment. The reflections appear
  at lower $q_z$ values, they are more intense and the shape of its cross-sections, 
  especially in the $q_r$ direction are different relative to the experimental system
  (See Figure~\ref{fig:rpi_exp_comparison} where we used cross-sections of the simulated
  XRD generated from the ordered parallel displaced configuration as an example). In 
  this section, we explore the various contributions to these discrepancies, and use what
  we've learned to speculate on improvements to our initial configurations and simulation
  procedures.

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{exp_rsection_fit.png}
  \caption{FWHM = 0.792 $\pm$ 0.009 $\AA^{-1}$}\label{fig:exp_rsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sim_rsection_fit.png}
  \caption{FWHM = 0.796 $\pm$ 0.011 $\AA^{-1}$}\label{fig:sim_rsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{exp_zsection_fit.png}
  \caption{FWHM = 0.110 $\pm$ 0.003 $\AA^{-1}$}\label{fig:exp_zsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sim_zsection_fit.png}
  \caption{FWHM = 0.163 $\pm$ 0.011 $\AA^{-1}$}\label{fig:sim_zsection_fit}
  \end{subfigure}
  \caption{
  The maximum intensity of R-$\pi$ generated from simulations of the ordered
  parallel displaced configuration is 3 times larger than experiment. The $q_r$
  cross-section of R-$\pi$ ((a) and (b)) is qualitatively different between 
  experiment (a) and simulation (b). We fit Lorentzian profiles to each peak and
  the FWHM of the simulated pattern agrees with experiment within error, however
  the fit to the simulated data is obscured by the three sharp peaks which appear
  near $q_r$ = 0. The $q_z$ cross-sections of R-$\pi$ ((c) and (d)) are 
  qualitatively similar. Each fits a Lorentzian profile well, however the FWHM
  of the simulated cross-section (d) is 48\% larger than the experimental 
  cross-section. Additionally, peak of the simulated $q_z$ cross-section is 
  located at a lower $q_z$ value than experiment.}\label{fig:rpi_exp_comparison}
  \end{figure}

%  The difference in intensity ranges from 3 times too high in the ordered parallel
%  displaced system to 15 times too high in the ordered sandwiched configuration 
%  (Table~\ref{table:relative_inensities_300K}).

  R-$\pi$ appears at a lower $q_z$ value in our simulations versus experiment because
  monomers in the simulated system stack further apart than those in the experimental
  system (Table~\ref{table:correlation_length}). We calculated $z$-direction pair distribution
  functions, $g(z)$, as described in Section~\ref{section:correlation_length}.
  %BJC11: Below is in methods but might be worth restating here? 
%  based on the center of mass of each monomer head group. In order
%  to calculate $g(z)$, we averaged all $z$-slices of the 3D pair distribution function, $g(x, y, z)$, 
%  (Equation~\ref{eqn:correlation}) within
%  2.1 \AA~of $g(0, 0, z)$. In this way we are measuring correlation between head 
%  groups within the same column. 
  The resulting distributions are generally characterized
  by decaying oscillatory behavior where the average distance between peaks corresponds
  to the average distance between stacked monomer head groups (Figure~\ref{fig:correlation}).
  We calculated this equilibrated vertical stacking distance, $\mathit{d}_{equil}$, between
  monomers using Equation~\ref{eqn:decaying_sinusoid}. The distance between stacked
  monomers is greater than experiment by 0.5--0.9 \AA~across all cases, with disordered
  basins at the high part of that range, 0.2 and 0.3 \AA~more distant. This behavior is
  not surprising since GAFF models atoms as point charges and  % BJC11: need reference
  does not appropriately model the aromatic $\pi-\pi$ interactions which would make it
  more energetically favorable for the monomers to stack closer together. Additionally, 
  it is possible that the tails prevent close stacking of monomer head groups and we do
  not achieve the timescales necessary for them to rearrange into a necessarily more
  tightly packed configuration. We equilibrated the system at 500K then annealed it to 300K
  in an attempt to coerce the tails into a more tightly packed configuration, however 
  we saw no improvement over our 300K models. See section S-TBD for details.

  The system size, in the $z$-direction, does not significantly alter $g(z)$. 
  In Figure~\ref{fig:correlation}, oscillations do not fully decay, so a taller
  system may be necessary to fully capture the correlation function. We 
  equilibrated a sandwiched system with twice as many monomers per column 
  so that the system size doubled in the $z$-direction. The correlation length 
  increases modestly from 4.5 $\pm$ 0.4 to 7.3 $\pm$ 1.2 \AA. Visually, the
  correlation functions are nearly identical and oscillatory behavior persists
  throughout $g(z)$ in both cases (See Figure~S-\ref{S-fig:z_correlation_overlay}).

  The broadening of the $q_z$ cross-section of R-$\pi$ is related to $z$-directional
  correlation between scatters within monomer columns. One can determine the correlation length as the
  inverse of the full width at half maximum (FWHM) of the $q_z$ cross-section of R-$\pi$.
  Using this technique, we calculated the correlation length of the experimental system
  to be 9.0 \AA. As scatterers become less correlated, we expect that R-$\pi$ will broaden.

  The correlation lengths of vertically stacked scatterers in our atomistic simulations
  are in reasonable agreement with experiment. Since it is not feasible for us to
  simulate membranes with much taller columns, for increased $q_z$ resolution of our
  simulated XRD patterns, and because the simulated peak shape is convoluted by the
  extremely intense maximum of R-$\pi$, we measured correlation length by fitting
  Equation~\ref{eqn:decaying_exponential} to the peaks of $g(z)$. The correlation 
  length of the parallel displaced, ordered basin system shows the closest agreement
  with experiment (Table~\ref{table:correlation_length}). 
  %BJC11: below might confuse the reader
%  Note that its correlation length
%  ($L$ = 14.5 \AA) is larger than what we would expect by inverting the FWHM of the $q_z$
%  cross-section of R-$\pi$ shown in Figure~\ref{fig:sim_zsection_fit} ($L$ = 1 / 0.163 
%  = 6.1 \AA). The reason is likely a combination of artificial broadening caused by the
%  overlap of R-alkanes and R-$\pi$ as well as uncertainty in the fit due to low simulated
%  XRD resolution.
   We could not extract a reliable correlation
  length from the disordered parallel displaced configuration since the peaks do not show
  clear patterns that can easily be fit to an exponential decay. The correlation length
  of both sandwiched systems are relatively low because the height of the first peak of 
  $g(z)$ is so high.
